Underdispersion in the context of community athletics

### 2024-03-28 inst/parkrun_idea.Rmd
save the matrix, optionally calculate from scratch

getlike <- function(v){
  alpha <- v[1]
  beta <- v[2]
 c(
tabulate(replicate(10000,which(rrace(setNames(f(26,alpha),letters))==letters[beta])),nbins=26)
,alpha,beta)
}
```

```{r calculateLikemat,cache=TRUE}

alpha_try <- seq(from=1,to=6,len=10)
beta_try <- 1:26

M <- as.matrix(expand.grid(alpha=alpha_try, beta=beta_try))
system.time(L <- t(apply(M,1,getlike)))
L_integer <- L  # counts
L[,1:26] <- L[,1:26]/mean(rowSums(L[,1:26]))
colnames(L) <- c(letters,'alpha','beta')
head(L)
```

@@

```{r}
plot(table(L_integer[,1:26]))
```

>>>>

getlike <- function(v){
  alpha <- v[1]
  beta <- v[2]
 c(
tabulate(replicate(1000,which(rrace(setNames(f(26,alpha),letters))==letters[beta])),nbins=26)
,alpha,beta)
}
```

```{r calculateLikemat,cache=FALSE}
alpha_try <- seq(from=1,to=6,len=10)
beta_try <- 1:26
calculate_from_scratch <- FALSE
if(calculate_from_scratch){
    M <- as.matrix(expand.grid(alpha=alpha_try, beta=beta_try))
    system.time(L <- t(apply(M,1,getlike)))
    colnames(L) <- c(letters,'alpha','beta')
    write.table(L,file="likelihoodmatrix.txt")
} else {
    L <- read.table("likelihoodmatrix.txt")
}
L_integer <- L  # counts
L[,1:26] <- L[,1:26]/mean(rowSums(L[,1:26]))
head(L_integer)
```

@@

```{r}
#plot(table(L_integer[,1:26]))
```
